% !TEX root = ../thesis-example.tex
%
\part{Methodology}

\chapter*{Overview}
\label{sec:methods}

\cleanchapterquote{Wer anderen einen Bratwurst brät, hat ein Bratwurstbratgerät.}{Autor unbekannt}{}

The general story line should be like this:
\begin{enumerate}
	\item
		\emph{Advanced 2D Ultrasound Visualization}: IEEEVis'15 paper on uncertainty visualization for B-mode US
	
	\item
		\emph{Advanced Ultrasound Processing/Compounding}: IPCAI'14 paper on orientation-driven ultrasound compounding in order to generate high quality 3D US volumes
	
	\item
		\emph{Advanced 3D Ultrasound Visualization}: IEEEVis'14 paper on Predicate-based visualization
\end{enumerate}

These are my three main papers for the thesis. Other related work might be considered to be included as well:
\begin{itemize}
	\item
		\emph{Prostate biopsy visualization}: Though this is mostly Oliver's and Amit's work, it is closely related to my thesis topic. Furthermore, the visualization was implemented in CAMPVis and with my help. Thus I could talk about multi-modal visualization and how intra-operative US visualization can be helpful.
		
	\item
		\emph{Uncertainty Visualization for 3D Ultrasound}: So far, I have not worked on this. Nevertheless, this would be a nice bridge section between 1 and 2+3 from above. Also Nassir suggested this. Thus, I should consider adding at least a generic section/chapter on this, discussing possible approaches, however without an in-depth evaluation.
		
	\item
		\emph{Schematic Neuro Electrode Map}: This is a really nice piece of work, however, not related at all to the thesis topic. Furthermore, the work is at least 50\% from Jakob and already published in his Bachelor's thesis. Thus, an in-depth discussion of this as part of this thesis is doubtful.
	
	\item
		\emph{3D Velocity Field and Flow Profile Reconstruction from Arbitrarily Sampled Doppler Ultrasound Data}: This is also originally Oliver's work to which I only contributed parts of the visualization. I could briefly mention this piece of work as example for flow visualization - since it is at least connected to US.
\end{itemize}

Finally, I could have an extra section on software frameworks for medical Visualization, namely CAMPVis. There, I could discuss design and implementation decisions. Since CAMPVis is a huge part of my work with the chair, I should check whether such a chapter makes sense in a PhD thesis at our chair.



