% !TEX root = ../thesis-example.tex

\chapter{Personal Perception in the Magic Mirror Framework}
%why we develop a magic mirror framework: the advantage of magic mirror: to create a personal perception of the medical information
The General Medical Council recently proposed standards for effective teaching and learning of medical students \cite{Council2009}. They stated that: ``...medical schools should take advantage of new technologies…. to deliver teaching.'' Augmented reality research has matured to a level that its applications can now be found in both mobile and non-mobile devices \cite{Bacca2014} and research on AR has also demonstrated its extreme usefulness for increasing student motivation in the learning process \cite{Chang2014,DiSerio2013}. Providing adequate learning experience to different learners is a challenging issue as the learning system generally does not adapt content to suit individual learner needs. Personalization for promoting a multi-modal learning environment is also a growing area of interest, such as the development of user modeling and personalized processes which place the student at the center of the learning development.

Acquiring knowledge usually involves reading big and heavy books containing static images with accompanying text information. This information, both the text and the
images, has to be learned by heart. The Internet provides an additional source of data, but the process of memorizing it has not changed. In the case of learning anatomy in particular, the theoretical knowledge from books and online sources are supported by practical experience gained from performing autopsies on corpses, but it can be difficult to observe certain processes in the living organism, like the activity of working muscles.

By presenting a virtual representation of the subject matter and at the same time creating a direct connection between the information the user wants to learn and his own body and activities, Augmented Reality could help understand and memorize complex processes, and either supplement conventional learning or even supersede it altogether. Previous systems on AR visualization of anatomy used expensive systems involving HMDs. The system presented in this chapter in an inexpensive and easy to use AR system, which takes advantage of the magic mirror concept to present medical information about human anatomy. It presents anatomical data augmented onto the user's body and it shows additional 2D and 3D information according to the need. The magic mirror concept provide the user `the superman ability' to look through his/her own body. It enables the medical information to be perceived naturally linking to a real human body. Natural gesture is chosen as the interaction methodology, and interaction with the AR view of the user's own body provides a personal perception in the magic mirror framework.

%the works we have done in this chapter: to improve the personal perception, we do collect personal information to improve the registration and interaction Mixed reality
The magic mirror framework for anatomy education is firstly presented in Section \ref{sec:3-PPMM:MMC}, including the hardware setup, the software framework and some important system features. A personal perception framework for medical education is created using the magic mirror conception, and a survey with 72 fresh medical students was done to evaluate the conception and find the direction to improve the system. In Section \ref{sec:3-PPMM:Registration}, the user specific information is collected to improve the registration of the AR view and a more accurate magic mirror view enhances the personal perception. Section \ref{sec:3-PPMM:IMR} takes the advantage of the interactive mixed reality to generate a personalized learning procedure, and systems are implemented and evaluated for anatomy leaning, especially for muscle learning. At last some serious games are developed in the magic mirror framework for health-care education and rehabilitation.

\input{content/3-MMC}
\input{content/3-PRMM}
\input{content/3-IMR}