% !TEX root = ../thesis-example.tex
%
\pdfbookmark[0]{Acknowledgments}{Acknowledgments}
\chapter*{Acknowledgments}
\label{sec:acknowledgement}

%Coming to Germany, Munich, TUM, and CAMP, as an outsider - as well as focusing on a related but different topic than others - I learn a lot during these four years.
%Performing a PhD abroad is a one-of-a-kind experience and while being in the process we have to struggle with quite a few issues, including research and culture.
%At the same time, certainly every PhD process is unique and everybody copes with the upcoming challenges differently.
Obtaining a PhD abroad is a unique and exciting experience and while being in this process we are sometimes faces with different challenges, including research and culture. To facilitate my integration in a new country and offering me a world-class research environment, I would like to thank Prof. Nassir Navab and Dr. Pascal Fallavollita and express my great respect and deep appreciation to them. Thanks very much for the incredible amount of freedom and guidance they provided me for my work. I also want to express my thanks to my teachers Prof. Yong Dou and Prof. LunGuo Xie, and China Scholarship Council (CSC) for their supports. 

Secondly, I want to thank my wife Dehua Kong and my family, who always supported me in the last four years. They did a lot for me and I would not finish my studies without their understanding and help.

Furthermore, I would like to thank Severine Habert, Philipp Stefan, Patrick Wucherer, Xiang Wang, Ulrich Eck, Felix Bork, Hemal Naik, and Hessam Roodaki for their incredibly valuable support as colleagues. I really appreciate Jakob Weiss, Philipp Jutzi, Kevin Merckx, Sabahattin Giritli, Yisong Qiao, Florian Reichhold, and Kevin Yu, who did very good job with me during their bachelor or master thesis.

Finally, I want to express my gratitude to my friends, Zhu Tang, Yuxiang Chen, Qi Lv, Xuan Li, Lejing Wang, Hanyin Sun, and Meng Luo.


